%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Recent Presentations \& Seminars}


\begin{pubentries}
\begin{\small}

\textbf{Invited}
\begin{longtable}{ l p{\textwidth - 2.5cm} }
\honordatestyle{2018} & \skillsetstyle{How spatiotemporal environmental heterogeneity impacts population, community, and ecosystem dynamics. \emph{Division of Biology}, Kansas State University. (\emph{forthcoming})} \\
\honordatestyle{2018} & \skillsetstyle{Spatiotemporal forecasting of plant populations and a proposal for partitioning forecast uncertainty. \emph{American Statistical Association ENVR Workshop: Statistics for the Environment: Research, Practice and Policy}, Asheville, NC.} \\
\honordatestyle{2018} & \skillsetstyle{What determines ecosystem stability in theory and in nature? \emph{Odum School of Ecology}, University of Georgia.} \\
\honordatestyle{2018} & \skillsetstyle{Advancing ecological forecasting. \emph{Center for the Ecology of Infectious Diseases}, University of Georgia.} \\
\honordatestyle{2018} & \skillsetstyle{What determines ecosystem stability in theory and in nature? \emph{Department of Botany}, University of Hawai'i at Mānoa.} \\
  \honordatestyle{2017} & \skillsetstyle{What determines ecosystem stability in theory and in nature? \emph{Quinney College of Natural Resources}, Utah State University.} \\
  \honordatestyle{2013} & \skillsetstyle{Sustainability and Biome-Level Impacts of Fuelwood Harvesting in sub-Saharan Africa. \emph{Geospatial Center of Excellence}, South Dakota State University.} \\
\end{longtable}

\textbf{Contributed}
\begin{longtable}{ l p{\textwidth - 2.5cm} }
  \honordatestyle{2017} & \skillsetstyle{The relationship between species richness and ecosystem variability is shaped by the mechanism of coexistence. \emph{ESA Annual Meeting}, Portland, OR.} \\
  \honordatestyle{2016} &  \skillsetstyle{Disentangling the drivers of species synchrony in natural plant communities: Environmental forcing, demographic stochasticity, and interspecific interactions. \emph{ESA Annual Meeting}, Fort Lauderdale, FL.} \\
  \honordatestyle{2015} & \skillsetstyle{Do we need detailed demographic data to forecast population responses to climate change? \emph{ESA Annual Meeting}, Baltimore, MD.} \\
  \honordatestyle{2014} & \skillsetstyle{Africa’s Fuelwood Footprint and the Biome-Level Impacts of Tree Harvest. \emph{Center for Biodiversity Theory \& Modeling, CNRS}, Moulis, France.} \\
  \honordatestyle{2014} & \skillsetstyle{Forecasting climate change impacts on plant population dynamics at large spatial extents: a test case with sagebrush (\emph{Artemisia}) species. \emph{ESA Annual Meeting}, Sacramento, CA.}
\end{longtable}

\end{pubentries}