%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Manuscripts in review}


\begin{pubentries}
\begin{\small}
Dietze, M.C., A. Fox, L. Beck-Johnson, J.L. Betancourt, M.B. Hooten, C.S Jarnevich, T. Keitt, M.A. Kenney, C.M. Laney, L.G. Larsen, H.W. Loescher, C.K. Lunch, B. Pijanowski, J.T. Randerson, E.K. Read, {\bf{A.T. Tredennick}}, R. Vargas, K.C. Weathers, \& E.P. White. (In revision). Iterative near-term ecological forecasting: Needs, opportunities, and challenges. \emph{Proceedings of the National Academy of Sciences} (Previous decision: ``Minor Revisions'').\\
\\
{\bf{Tredennick, A.T.}}, A.R Kleinhesselink, J.B. Taylor, \& P.B. Adler. (In revision). Ecosystem functional response across precipitation extremes in a sagebrush steppe. \emph{PeerJ} (Previous decision: ``Major Revisions'').

\end{pubentries}


\cvsection{Manuscripts in preparation}
\\
\emph{Available upon request}
\begin{pubentries}
\begin{\small}
\\
Adler, P.B., D. Smull, K.H. Beard, R.T. Choi, T. Furniss, A. Kulmatiski, {\bf{A.T. Tredennick}}, \& K.E. Veblen. (In preparation). Competition and coexistence in plant communities: is intraspecific competition stronger than interspecific competition?\\
\\
{\bf{A.T. Tredennick}}, B.J. Teller, P.B. Adler, G. Hooker, \& S.P. Ellner. (In preparation). Individual size affects responses to environmental variation, but the population-level consquences are small.\\
\\
Bucini, G., N.P. Hanan, {\bf{A.T. Tredennick}}, S. Saatchi, M.A. Lefsky, E. Mitchard, \& L-J Theron. (In preparation). Woody cover mapping in Africa: combining optical and radar remote sensing for improved prediction in open savannas.\\
\\
{\bf{Tredennick, A.T.}}, N.P. Hanan, G. Bucini, \& L. Prihodko. (In preparation). No evidence that savanna and forest are alternative stable states at large spatial scales in sub-Saharan Africa.


%---------------------------------------------------------
\end{pubentries}